---
title: "What the Package Does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the Package Does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Noah2025)
```

# Introduction

# Functions

The `lmSummaryStats()` function calculates three key statistics from a linear model:

- **TSS**: Total Sum of Squares
- **MSS**: Model Sum of Squares
- **RSS**: Residual Sum of Squares

Example:

```{r lm-example}
# Create a sample dataset
set.seed(123)
df <- data.frame(
  x = rnorm(100, mean = 50, sd = 10),
  y = 5 + 2 * rnorm(100, mean = 50, sd = 10) + rnorm(100, mean = 0, sd = 5)
)
# Fit a linear model
model <- lm(y ~ x, data = df)

# Get summary stats
lmSummaryStats(model)
```

This will return a list of the TSS, MSS, and RSS of the linear model. 

## mybin

The `mybin()` function creates a plot and returns a table of probabilities of getting i successes out of n trials with a specified probability of success using a simulation. 

Example:

```{r}
mybin(10000, 10, 0.8)
```

This will create a plot of the number of expected successes in the binomial solution, and print these values to the console.

## myboot2

The `myboot2()` function will use bootstrapping to find a confidence interval for a statistic using a random sample. 

Example:

```{r}
myboot2(iter=1000, x=runif(20, 1, 10), fun="mean", alpha=0.05)
```

This will plot a histogram of the bootstrap samples, show the bootstrap confidence intervals and expected value, and returns the values from each of the simulations. 

## mycltb

The `mycltb()` function uses the central limit theorem to plot the distribution of the mean of samples of the binomial distribution.

Example:

```{r}
mycltb(n=10, iter=10000, p=0.3)
```

This will plot a histogram of the binomial outputs along with a line representing the binomial distribution, to show how well the two distributions match.

## mymaxlik

The `mymaxlik()` function will use a grid approximation to estimate the parameter that maximizes the log-likelihood function "lfun".

Example:

```{r}
lfun <- function(x, p) {
  dbinom(x,
         size = 20,
         prob = p,
         log = TRUE)
}

# Example data
x <- c(3, 3, 4, 3, 4, 5, 5, 4)

# Find the maximum likelihood
mymaxlik(lfun, x, seq(
  from = 0,
  to = 1,
  length.out = 100
))
```

In this example, we created our log function, some sample data, and ran the function. The function will output a plot of the log likelihood as a function of the parameter, and show which value on the grid maximizes the log likelihood. 

## myncurve

The `myncurve()` function plots a normal curve and gives the probability of a sample being less than a given value, `a`.

Example

```{r}
myncurve(10, 4, 6)
```

The function will output a graph of the normal distribution, along with a colored region that and the probability that the output of the distribution is less than this value. It will also returns the mean, standard deviation, and probability as a list.

## mysq

The `mysq()` function takes in a vector of numbers and returns a new vector where each entry is the square of the input entry.

Example:

```{r}
mysq(1:10)
```

Here, the function will returns a new vector containing the first 10 squares. 

## ntickets

The `ntickets()` function will determine the number of tickets to sell with a specified success rate, total number of seats, and overbooking chance tolerance. 

Example:

```{r}
ntickets(N=100, gamma=0.1, p=0.9)
```

The function outputs a graph of the object function vs n using a binomial distribution as well as when using a normal approximation. It also returns a list that includes the number of tickets to sell based on the binomial, based on the normal approximation, the number of seats available, the probability of a ticket buyer actually showing up to the flight, and the acceptable probability of overbooking. 

# Datasets

## fire

The fire dataset includes 15 entries, where each entry records a property's distance to the closest fire station (in miles) and the amount of damage that property received in a fire (in thousands of dollars).

```{r}
fire
```

